For Online Publication \\ Appendix for ``The Size Distribution of Firms and Industrial Water Pollution: A Quantitative Analysis of China''

### 2019-09-19 Documentation/DataAppendix_AEJ_Final.tex
results cohesive
ready for submission

% Set header and footer
\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhead{}
\fancyhead[LE,RO]{\thepage}
%\fancyhead[CE]{\textit{X. TANG}}
%\fancyhead[CO]{\textit{DATA APPENDIX: FIRM-SIZE AND POLLUTION}}
\cfoot{}
\renewcommand{\headrulewidth}{0pt}

@@

\begin{table}[t]
\footnotesize
\centering
\begin{threeparttable}
\caption{Percentage of Firms with Positive Emissions by Pollutants}
\begin{tabular}{lccccccccccc}
    \hline \hline
%    & Waste & COD & Petrochemicals & Ammonian & BOD & Cyanidum & Hex-Chromium & Phenol & Arsenium & Chromium \\
                    & Waste & COD  & Petro & $\text{NH}_4^+$ & BOD  & CN   & $\text{Cr}^{6+}$ & Phenol & As   & Cr      \\   %& Total\\
    \midrule
    Key Sources     & 76.2  & 73.2 & 31.4 & 25.2             & 17.5 & 4.90 & 4.86             & 2.42   & 2.27 & 2.01    \\ %& 106,067 \\
    Regular Sources & 35.2  & 28.3 & 7.91 & 6.49             & 2.56 & 0.13 & N/A              & 0.04   & 0.07 & N/A     \\  %& 814,937 \\
    \bottomrule
\end{tabular}
\begin{tablenotes}
     \footnotesize{\item[$\dagger$]
     Source: The 2007 National General Survey of Pollution Sources (NGSPS). The acronyms are respectively referring to: Wastewater, Chemical Oxygen Demand, Petrochemicals, Ammonian, Biochemical Oxygen Demand, Cyanidium, Hexavalent Chromium, Volatile Phenols, Arsenium and Chromium.}
\end{tablenotes}
\label{tab:nfirmPollutant}
\end{threeparttable}
\end{table}

@@

The second and perhaps more important implication is that the ratio of treatment technology expenditure over output should decrease with the size of the firm. We find that it is also the case in the NGSPS data. For firms in the top-5 polluting industries, we calculate the average of the ratio of treatment equipment expenditure to output value within each quintile of output. The means of the ratio from the first (smallest) to the fifth (largest) quintile are 22\%, 11\%, 6.7\%, 5.0\%, and 2.7\%, respectively. A linear regression model that controls for the same set of covariates as in the main text delivers the same message:
%The second and perhaps more important implication is that treatment technology investment cost should decrease with the size of the firm. We find that it is also the case. By using the NGSPS, for firms in the top-5 polluting industries, we calculate the average of the ratio of treatment equipment expenditure to output value within each quintile of output. The means of the ratio from the first (smallest) to the fifth (largest) quintile are respectively 22\%, 11\%, 6.7\%, 5.0\%, and 2.7\%. A linear regression model controlling for the same set of covariates as in the main text delivers the same message
\begin{equation*}
    \log \left(\frac{\text{Investment}_i}{\text{Output}_i} \right) = \underset{(0.11)}{-0.73} - \underset{(0.004)}{0.40} \times \log (\text{Output}_i) + \vec{X} \gvec{\upgamma} + \varepsilon_i,
\end{equation*}
which shows a negative correlation as well. Together, the evidence supports our choice of modeling the adoption cost of clean technology as a fixed cost.

\textit{Prices of Physical versus Biological Equipment.}---We assume in the main text that only the installation of biological technologies requires a fixed cost. Here we provide evidence in support of this choice. The distributions of the prices for physical and biological equipments in absolute term (in CNY 10,000) are listed in Table \ref{tab:fixcosts_appen}.
\begin{table}[t]
    \footnotesize
    \centering
    \begin{threeparttable}
    \caption{Prices of Different Treatment Equipments}
    \begin{tabular}{lccccc}
    \hline \hline
    Technologies    & 25\%      & 50\%      & 75\%      & Maximum   & Mean \\
    \midrule
    Physical        & 2      & 6      & 25    & 800   & 36.14 \\
    Biological      & 30     & 85     & 260    & 4000   & 249.90 \\
    \bottomrule
    \end{tabular}
    \floatfoot{Source: 2007 NGSPS. All the numbers are measured in CNY 10,000.}
    \label{tab:fixcosts_appen}
    \end{threeparttable}
\end{table}
As is shown in the table, the prices of biological equipments are 7 to 15 times of those of physical equipments. In addition, the total installation costs of physical equipment for the top-5 polluting industries over those of biological equipment is only 0.087. %, implying that the installation costs of physical equipment when aggregated across the economy are only 9\% of those of the biological equipments. These evidence suggest that comparing to biological equipment, the costs of installing physical treatment equipments are small. Therefore in our model we assume that only the adoption of biological equipment is costly.%In addition, the total investment of physical equipment over biological equipment is 0.087, meaning that the installation costs of physical equipments when aggregated across the economy are only 9\% of those of the biological equipments. These evidence suggest that comparing to biological equipment, the costs of installing physical treatment equipments are small. Therefore in our model we assume that only the adoption of biological equipment is costly.
These facts again point to the importance of the fixed costs associated with the adoption of the clean technology. Therefore in our model we assume that only the adoption of biological equipment is costly.\footnote{In fact, what is crucial here is that the cost to install clean technology is higher than that of dirty technology.} %and support our somewhat extreme assumption that only the installation of biological technologies requires a fixed cost.

@@

\begin{table}[t]
\footnotesize
\centering
\begin{threeparttable}
\caption{Size Distribution on Pollution}
\begin{tabular}{lccccccc}
    \hline \hline
    Methods             & Paper  & Agricultural Food   & Textile    & Chemistry    & Beverage     & Average \\
    \midrule
    Non-parametric      & 39.8\% & 60.7\%              & 81.6\%     & 102.5\%      & 103.7\%      & 63.5\%  \\
    Piecewise-linear    & 34.8\% & 69.4\%              & 93.5\%     & 180.1\%      & N/A\tnote{a} & 75.4\%  \\
    Parametric          & 43.5\% & 61.1\%              & 97.5\%     & 101.2\%      & 89.0\%       & 67.0\%  \\
    \bottomrule
\end{tabular}
\begin{tablenotes}
     \footnotesize{
     \item[$\dagger$]
     Note: For individual industries, the numbers reported are the pollution intensity from using the U.S. firm size distribution as percentage of that using China's distribution. We use the 1st and 3rd quartile as the ends of the output range corresponding to each employment bin in the non-parametric calculation. Column 6 (Average) calculates the weighted average of these ratios using the percentage contribution in the first row of Table 1 in the main text as weights.}
     \item[a]
     Since the beverage industry has fewer firms than the others, there are employment size bins with no corresponding firms in China, which invalidates the method. We set the ratio to 100\% in the calculation of the last average.
\end{tablenotes}
\label{tab:accounting_appen}
\end{threeparttable}
\end{table}
\begin{enumerate}
  \item
  \textit{Non-parametric}:
    \begin{itemize}
    \item
    For each U.S. employment bin, we compute the 1st and 3rd quartile of output level for Chinese firms within that employment bin. The two quartiles are used as the lower and upper bounds for the output bins in NGSPS.
    \item
    We then use the median pollution intensity of firms within the newly defined output bins as the average pollution intensity for those bins.
    \item
    Lastly, we calculate the aggregate pollution by assigning to each bin the corresponding share of output. %The NGSPS production bins are used for China and the employment bins are used for U.S.
    \end{itemize}
  \item
  \textit{Piecewise Linear}:
  \begin{itemize}
    \item
    For each U.S. employment bin, we regress log-output on log-employment using the subset of Chinese firms within that employment bin. The lower and upper bounds for the output bins in this case are calculated as the predicted value of the above regression.
    \item
    We then run piecewise log-linear regression of pollution intensity on output within each new production bin. The average pollution intensity is chosen to be the predicted intensity at the midpoint of the new log-output bin.
    \item
    Lastly, the average intensity is applied to the output share distributions. %The U.S distribution does not change, however, a new distribution for China is calculated since the endpoints of the output bins are different.
    \end{itemize}
  \item
  \textit{Parametric}:
  \begin{itemize}
    \item
    Using the CNEC, we regress log-output on log-number of workers, which yields a {parametric} relationship between the number of workers and output.
    \item
    Using the NGSPS, we regress log-intensity on log-output, which yields a {parametric} relationship between intensity and output. From these two relationships, we can subsequently construct a new \emph{parametric} relationship between intensity and number of employees. The average intensity is chosen to be the midpoint of each U.S. employment bin. Notice that in this case we have a direct functional form for employment and intensity).
    \item
    Lastly, the average intensity is applied to the output share distributions. %The U.S. distribution does not change, but a new distribution for China is calculated since the endpoints of the production bins are different. Notice that this distribution for China is the one we use in Section \rom{1}.C.
\end{itemize}
\end{enumerate}

@@

\phantomsection
\addcontentsline{toc}{section}{REFERENCES}
\bibliography{D:/Dissertation/Literature/Dissertation1}
\bibliographystyle{aea}

>>>>

% Set header and footer
\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhead{}
\fancyhead[LE,RO]{\thepage}
\fancyhead[CE]{\textit{AMERICAN ECONOMIC JOURNAL: MACROECONOMICS}}
\fancyhead[CO]{\textit{QI ET AL.: FIRM SIZE DISTRIBUTION AND POLLUTION APPENDIX}}
\cfoot{}
\renewcommand{\headrulewidth}{0pt}

@@

\begin{table}[t]
\footnotesize
\centering
\begin{threeparttable}
\caption{Percentage of Firms with Positive Emissions by Pollutants}
\begin{tabular}{lccccccccccc}
    \hline \hline
%    & Waste & COD & Petrochemicals & Ammonian & BOD & Cyanidum & Hex-Chromium & Phenol & Arsenium & Chromium \\
                    & Waste & COD  & Petro & $\text{NH}_4^+$ & BOD  & CN   & $\text{Cr}^{6+}$ & Phenol & As   & Cr      \\   %& Total\\
    \midrule
    Key Sources     & 76.2  & 73.2 & 31.4 & 25.2             & 17.4 & 4.90 & 4.86             & 2.42   & 2.28 & 2.01    \\ %& 106,067 \\
    Regular Sources & 35.2  & 28.3 & 7.91 & 6.49             & 2.56 & 0.13 & N/A              & 0.04   & 0.07 & N/A     \\  %& 814,937 \\
    \bottomrule
\end{tabular}
\begin{tablenotes}
     \footnotesize{\item[$\dagger$]
     Source: The 2007 National General Survey of Pollution Sources (NGSPS). The acronyms are respectively referring to: Wastewater, Chemical Oxygen Demand, Petrochemicals, Ammonian, Biochemical Oxygen Demand, Cyanidium, Hexavalent Chromium, Volatile Phenols, Arsenium and Chromium.}
\end{tablenotes}
\label{tab:nfirmPollutant}
\end{threeparttable}
\end{table}

@@

The second and perhaps more important implication is that the ratio of treatment technology expenditure over output should decrease with the size of the firm. We find that it is also the case in the NGSPS data. For firms in the top-5 polluting industries, we calculate the average of the ratio of treatment equipment expenditure to output value within each quintile of output. The means of the ratio from the first (smallest) to the fifth (largest) quintile are 23\%, 11\%, 6.7\%, 5.0\%, and 2.7\%, respectively. A linear regression model that controls for the same set of covariates as in the main text delivers the same message:
%The second and perhaps more important implication is that treatment technology investment cost should decrease with the size of the firm. We find that it is also the case. By using the NGSPS, for firms in the top-5 polluting industries, we calculate the average of the ratio of treatment equipment expenditure to output value within each quintile of output. The means of the ratio from the first (smallest) to the fifth (largest) quintile are respectively 22\%, 11\%, 6.7\%, 5.0\%, and 2.7\%. A linear regression model controlling for the same set of covariates as in the main text delivers the same message
\begin{equation*}
    \log \left(\frac{\text{Investment}_i}{\text{Output}_i} \right) = \underset{(0.11)}{-0.73} - \underset{(0.004)}{0.40} \times \log (\text{Output}_i) + \vec{X} \gvec{\upgamma} + \varepsilon_i,
\end{equation*}
which shows a negative correlation as well. Together, the evidence supports our choice of modeling the adoption cost of clean technology as a fixed cost.

\textit{Prices of Physical versus Biological Equipment.}---We assume in the main text that only the installation of biological technologies requires a fixed cost. Here we provide evidence in support of this choice. The distributions of the prices for physical and biological equipments in absolute term (in CNY 10,000) are listed in Table \ref{tab:fixcosts_appen}.
\begin{table}[t]
    \footnotesize
    \centering
    \begin{threeparttable}
    \caption{Prices of Different Treatment Equipments}
    \begin{tabular}{lccccc}
    \hline \hline
    Technologies    & 25\%      & 50\%      & 75\%      & Maximum   & Mean \\
    \midrule
    Physical        & 1.4       & 3.5       & 10        & 1000      & 12.4 \\
    Biological      & 20        & 50        & 120       & 3056      & 109.6 \\
    \bottomrule
    \end{tabular}
    \floatfoot{Source: 2007 NGSPS. All the numbers are measured in CNY 10,000.}
    \label{tab:fixcosts_appen}
    \end{threeparttable}
\end{table}
As is shown in the table, the prices of biological equipments are 7 to 15 times of those of physical equipments. In addition, the total installation costs of physical equipment for the top-5 polluting industries over those of biological equipment is only 0.087. %, implying that the installation costs of physical equipment when aggregated across the economy are only 9\% of those of the biological equipments. These evidence suggest that comparing to biological equipment, the costs of installing physical treatment equipments are small. Therefore in our model we assume that only the adoption of biological equipment is costly.%In addition, the total investment of physical equipment over biological equipment is 0.087, meaning that the installation costs of physical equipments when aggregated across the economy are only 9\% of those of the biological equipments. These evidence suggest that comparing to biological equipment, the costs of installing physical treatment equipments are small. Therefore in our model we assume that only the adoption of biological equipment is costly.
These facts again point to the importance of the fixed costs associated with the adoption of the clean technology. Therefore in our model we assume that only the adoption of biological equipment is costly.\footnote{In fact, what is crucial here is that the cost to install clean technology is higher than that of dirty technology.} %and support our somewhat extreme assumption that only the installation of biological technologies requires a fixed cost.

@@

\begin{table}[t]
\footnotesize
\centering
\begin{threeparttable}
\caption{Size Distribution on Pollution}
\begin{tabular}{lccccccc}
    \hline \hline
    Methods             & Paper  & Agricultural Food   & Textile    & Chemistry    & Beverage     & Average \\
    \midrule
    Non-parametric      & 39.8\% & 60.7\%              & 81.6\%     & 102.5\%      & 103.8\%      & 63.5\%  \\
    Piecewise-linear    & 34.8\% & 69.4\%              & 93.5\%     & 180.2\%      & N/A\tnote{a} & 75.4\%  \\
    Parametric          & 43.5\% & 61.1\%              & 97.5\%     & 101.2\%      & 89.0\%       & 67.0\%  \\
    \bottomrule
\end{tabular}
\begin{tablenotes}
     \footnotesize{
     \item[$\dagger$]
     Note: For individual industries, the numbers reported are the pollution intensity from using the U.S. firm size distribution as percentage of that using China's distribution. We use the 1st and 3rd quartile as the ends of the output range corresponding to each employment bin in the non-parametric calculation. Column 6 (Average) calculates the weighted average of these ratios using the percentage contribution in the first row of Table 1 in the main text as weights.}
     \item[a]
     Since the beverage industry has fewer firms than the others, there are employment size bins with no corresponding firms in China, which invalidates the method. We set the ratio to 100\% in the calculation of the last average.
\end{tablenotes}
\label{tab:accounting_appen}
\end{threeparttable}
\end{table}
\begin{enumerate}
  \item
  \textit{Non-parametric}:
    \begin{itemize}
    \item
    For each U.S. employment bin, we compute the 1st and 3rd quartile of output level for Chinese firms within that employment bin. The two quartiles are used as the lower and upper bounds for the output bins in NGSPS.
    \item
    We then use the median pollution intensity of firms within the newly defined output bins as the average pollution intensity for those bins.
    \item
    Lastly, we calculate the aggregate pollution by assigning to each bin the corresponding share of output. %The NGSPS production bins are used for China and the employment bins are used for U.S.
    \end{itemize}
  \item
  \textit{Piecewise Linear}:
  \begin{itemize}
    \item
    For each U.S. employment bin, we regress log-output on log-employment using the subset of Chinese firms within that employment bin. The lower and upper bounds for the output bins in this case are calculated as the predicted value of the above regression.
    \item
    We then run piecewise log-linear regression of pollution intensity on output within each new production bin. The average pollution intensity is chosen to be the predicted intensity at the midpoint of the new log-output bin.
    \item
    Lastly, the average intensity is applied to the output share distributions. %The U.S distribution does not change, however, a new distribution for China is calculated since the endpoints of the output bins are different.
    \end{itemize}
  \item
  \textit{Parametric}:
  \begin{itemize}
    \item
    Using the CNEC, we regress log-output on log-number of workers, which yields a {parametric} relationship between the number of workers and output.
    \item
    Using the NGSPS, we regress log-intensity on log-output, which yields a {parametric} relationship between intensity and output. From these two relationships, we can subsequently construct a new \emph{parametric} relationship between intensity and number of employees. The average intensity is chosen to be the midpoint of each U.S. employment bin. Notice that in this case we have a direct functional form for employment and intensity).
    \item
    Lastly, the average intensity is applied to the output share distributions. %The U.S. distribution does not change, but a new distribution for China is calculated since the endpoints of the production bins are different. Notice that this distribution for China is the one we use in Section \rom{1}.C.
\end{itemize}
\end{enumerate}

@@

\phantomsection
\addcontentsline{toc}{section}{REFERENCES}
\bibliography{./Dissertation1}
\bibliographystyle{aea}
